%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\profilepic{} % Profile picture, just write inside brackets the name of the file of the profile pic you want to use

\cvname{\huge Facundo Uriona\newline\newline} % Your name

\cvjobtitle{Full-Stack Developer} % Job title/career

\cvdate{24 June 1999} % Date of birth
\cvaddress{Argentina} % Short address/location, use \newline if more than 1 line is required
\cvsite{https://github.com/urionafacu} % Personal website
\cvmail{urionafacu@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	 ABOUT ME
%----------------------------------------------------------------------------------------
	
\aboutme{Versatile and adaptable Full-Stack Developer with experience in a fast-paced e-commerce startup environment. Demonstrated expertise in full-stack development, with a strong focus on mobile and web applications, backend systems, and cloud technologies. Proven ability to quickly learn and implement new technologies, lead projects from conception to deployment, and drive innovation in product development.} % To have no About Me section, just remove all the text and leave \aboutme{}

\interests{I want to work in a company which always faces new challenges, so that I will be able to grow professionally and personally. Besides, I would love to be part of a great team using new technologies to keep myself updated.}

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}
\newline\newline 
{\large\underline{Full Stack Developer: Vitau (YC)}}  \hspace*{105pt}  Oct-2020 - Present
\newline\newline
{\textit{Role: Product Software Developer}} \hspace*{131pt} Apr-2022 to Present
    \newline- Optimize responsive web UIs with React/Next.js, boosting UX.
    \newline- Develop and maintain backend systems using Django.
    \newline- Guarantee reliability through pytest unit tests for features and fixes.
    \newline- Maintain and deploy React Native apps, enhancing stability and features.
    \newline- Deploy API Gateway and Lambda, streamlining serverless scalability.
    \newline- Set up secure SFTP on EC2 for data transfer and storage in S3.
    \newline- Containerize applications with Docker for AWS Fargate deployment.
    \newline- Develop a Go microservice for compressing multimedia files (PDF, PNG, JPG, etc), exploring new language capabilities.
    \newline- Automate and optimize backend processes with scheduled Celery tasks.
    \newline- Provide business insights via on-demand SQL queries in Metabase for non-technical teams.
    \newline- Guide API onboarding for third-party integrations with technical support.
    \newline- Maintain product quality by resolving Sentry-reported errors via Slack channels across platforms.
    \newline\newline\textit{\underline{Tools:} Django, Next.js, React Native, AWS, Postgres \underline{Methodology:} Agile}
    \newline\newline
{\textit{Role: Frontend \&\ Mobile Developer}} \hspace*{97pt} Oct-2020 to Apr-2022
    \newline- Built and launched App MVP with Expo, React Native, and TypeScript in 6 months.
    \newline- Designed scalable UI using Atomic Design principles.
    \newline- Managed global state with Zustand and Immer.
    \newline- Enhanced data handling with React Query. 
    \newline- Implemented E2E testing with Cypress, automated via GitHub Actions CI for every production release.
    \newline- Integrated reactive search for real-time product discovery.
    \newline- Secured user access with JWT authentication, using OS-level secure storage for refresh tokens.
    \newline- Automated linting, formatting, and TypeScript checks with Husky pre-commit hooks.
    \newline- Increased component reusability with HOCs and custom hooks.
    \newline- Managed native integrations with Expo pre-builds.
    \newline- Managed OTA and app store releases.
    \newline- Implemented deep linking to mirror website navigation, ensuring seamless user experience across platforms.
    \newline- Configured Google Analytics/Mixpanel for user tracking and behavior analysis.
\newline\newline\textit{\underline{Tools:} React Native, TypeScript, Zustand, React Query \underline{Methodology:} Agile}
\newline\newline

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem {}{Systems Engineering - Studies}{2017-2020}{Universidad Tecnológica Nacional (UTN)}

\end{twenty}


% \section{Courses}


%  \begin{twenty}
%  \twentyitem{}{First Certificate Exam}{2012}{University of Cambridge}
%   \twentyitem{}{Data Science - Level: Advanced}{2019}{Universidad Austral}
%  \end{twenty}

\end{document} 